%\section{Lab Environment}


You need to use our provided virtual machine image for this lab.
The name of the VM image that supports this lab is called
{\tt SEEDUbuntu12.04.zip}, which is built in June 2014.
If you happen to have an older version of our pre-built VM image,
you need to download the most recent version, as the older version
does not support this lab. Go to our SEED web page
(\url{http://www.cis.syr.edu/~wedu/seed/})
to get the VM image.


\subsection{Environment Configuration}

In this lab, we need three things, which are already 
installed in the provided VM image: (1) the Firefox web browser,
(2) the Apache web server, and (3) the {\tt Elgg} 
web application. For the browser,
we need to use the \texttt{LiveHTTPHeaders} extension for Firefox to
inspect the HTTP requests and responses. The pre-built \ubuntu
VM image provided to you has already installed the Firefox web browser with the
required extensions. 


\paragraph{Starting the Apache Server.}
The Apache web server is also included in the pre-built \ubuntu
image. However, the web server is not started by default.
You need to first start the web server using the
following command:
\begin{verbatim}
   % sudo service apache2 start
\end{verbatim}

\paragraph{The {\tt Elgg} Web Application.}
We use an open-source web application called {\tt Elgg} in this lab.
{\tt Elgg} is a web-based social-networking application. 
It is already set up in the 
pre-built \ubuntu VM image. 
%If you want to try it yourself, here is a detailed online
%tutorial on how to install {\tt Collabtive} and configure its
%database~\cite{collabtive}. 
We have also created several user accounts on the {\tt Elgg} server and the credentials are given below.


\vspace{0.1in}
\begin{tabular}{|l|l|l|}
\hline
User 	& UserName 	& Password\\
\hline
Admin 	& admin 	& seedelgg \\
Alice 	& alice 	& seedalice \\
Boby 	& boby 		& seedboby \\
Charlie & charlie 	& seedcharlie \\
Samy 	& samy 		& seedsamy \\
\hline
\end{tabular}
\vspace{0.1in}


\paragraph{Configuring DNS.}
We have configured the following \urlorurls needed for this lab. To access 
the \urlorurls, the Apache server needs to be started first:
